\begin{thebibliography}{99}
  \addcontentsline{toc}{section}{References}
  
 \bibitem{area}Hannah Ritchie and Max Roser (2021) - "Forests and Deforestation". Published online at OurWorldInData.org. Retrieved from: 'https://ourworldindata.org/forests-and-deforestation' [Online Resource]
  
 \bibitem{article}Brunet-Navarro, P., Jochheim, H., Muys, B. The effect of increasing lifespan and recycling rate on carbon storage in wood products from theoretical model to application for the European wood sector. Mitig Adapt Strateg Glob Change 22, 1193–1205 (2017). https://doi.org/10.1007/s11027-016-9722-z
   
 \bibitem{1}Lourens Poorter  and Dylan Craven  and Catarina C. Jakovac  and Masha T. van der Sande  and Lucy Amissah  and Frans Bongers  and Robin L. Chazdon  and Caroline E. Farrior  and Stephan Kambach  and Jorge A. Meave, et al. Multidimensional tropical forest recovery[D]. Science,374(6573),2021:1370-1376, doi:10.1126/science.abh3629
  
 \bibitem{2}Börje Kyrklund. The potential of forests and forest industry in reducing excess atmospheric carbon dioxide[N/OL]. Food and Agriculture Organization of the United Nations. https://www.fao.org/3/u0700e/u0700e04.htm
  
 \bibitem{3}Charlotte E. Wheeler, Patrick A. Omeja, Colin A. Chapman, Martin Glipin, Charles Tumwesigye, Simon L. Lewis,Carbon sequestration and biodiversity following 18years of active tropical forest restoration[J],Forest Ecology and Management,Volume 373,2016:44-55,https://doi.org/10.1016/j.foreco.2016.04.025.
  
 \bibitem{4}Kotaro Iizuka and Ryutaro Tateishi. Estimation of CO2 Sequestration by the Forests in Japan by Discriminating Precise Tree Age Category using Remote Sensing Techniques[J]. Remote Sensing,2015,7,15082-15113; doi:10.3390/rs71115082
  
 \bibitem{5}Meenakshi Kaul, G. M. J. Mohren and V. K. Dadhwal. Carbon storage and sequestration potential of selected tree species in India[J].Mitig Adapt Strateg Glob Change,(2010),15:489–510
 
 \bibitem{7}Food and Agriculture Organization of the United Nations. Climate change and forests[J/OL].https://www.fao.org/3/y0900e/y0900e06.htm
 
 \bibitem{8}Institut national de l’information géographique et forestière. Growing-stock volume and distribution[J/OL].https://inventaire-forestier.ign.fr/spip.php?rubrique86
  
 \bibitem{physics}David J. Griffiths. Introduction to Electrodynamics[M]. Prentice Hall:United States of America,1999:39-50.
  
 \bibitem{literature}D. Hawksworth. Global species numbers of fungi: are tropical studies and molecular approaches contributing to a more robust estimate[J]. Biodiversity and Conservation,2012.
  
 \bibitem{R2}Hiriote, Sasiprapa. Multivariate concordance correlation coefficient[D]. United States of America:The Pennsylvania State University,2009.
  
 \bibitem{logisticmodel}Nath, Gopal Chandra. Logistic regression model and case study[D]. United States of America:Lamar University - Beaumont,2014.
  
 \bibitem{multigroups}Shang, Justin. Model Assessments in Logistic Regression[D]. United States of America:University of Wyoming,2019.
  
 \bibitem{land}Ghuneim, Lydia-Ann John. Distribution, Diversity, and Function of Filterable Microorganisms in the Conwy River[D]. United Kingdom:Bangor University,2020.
  
 \bibitem{gray}Wu, Zhao Yang. Stock Index Prediction Based on Grey Theory, Arima Model and Wavelet Methods[D]. Canada:Concordia University,2010.
  
 \bibitem{population}Wikipedia. Biodiversity[EB/OL].https://simple.wikipedia.org/wiki/Biodiversity, 2021-1-16.
  
 \bibitem{carboncircle}Wikipedia. Carbon cycle[EB/OL].https://simple.wikipedia.org/wiki/Carbon\_cycle, 2021-1-16.
 
 \bibitem{value1}Pan Hua. Liu Xiaoyi . Economic Value Evaluation of Forest Ecosystem Service Function in Yunnan [J] Ecological economy, 2018,34 (05): 201-206 + 211.
 
 \bibitem{value2}Jiang Ziwei.Research on Value Accounting and Realization Path of Forest Ecological Assets [D] Nanhua University, 2021.
 
 \bibitem{plan} Amy, Grotta (May 2014). "Management Planning for Woodland Owners: Why and How". Revised April 2018.
  
 \bibitem{decision tree} Prashant, Gupta (18 May 2017). "Decision Trees in Machine Learning". Towards Data Science. Archived from the original on 10 December 2021. Retrieved 5 December 2021.
 \bibitem{data of forest}Hannah Ritchie and Max Roser (2021) - "Forests and Deforestation". Published online at OurWorldInData.org. Retrieved from: 'https://ourworldindata.org/forests-and-deforestation' [Online Resource]
 
\end{thebibliography}